Software Citation Principles

### 2016-07-25 sc-principles/software-citation-principles.tex
removed note from use case 16

\niemnote{add description; came from \url{https://github.com/force11/force11-scwg/issues/128}}
Domain and institutional data repositories have both data and software
artifacts, and want to link these together in a provenance trace that can
be cited. Sometimes the software is a separately identified artifact, but at
other times software is included inside of data packages, and the researcher
wants to cite the combined product.

>>>>

Domain and institutional data repositories have both data and software
artifacts, and want to link these together in a provenance trace that can
be cited. Sometimes the software is a separately identified artifact, but at
other times software is included inside of data packages, and the researcher
wants to cite the combined product.
